---
title: "p8105_hw6_hx2264"
author: "Hongyao Xie"
date: "November 20, 2018"
output: html_document
---

## Problem 1

```{r echo = FALSE}
library(tidyverse)
```

**Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved.**

```{r}
# Create a city_state variable
homic <-  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(city, state, sep = ",")) 

# Create a binary variable
homic$hmc_resolve <- ifelse(homic$disposition == "Closed by arrest", 1, 0)
```

**Omit cities Dallas, TX; Phoenix, AZ; Kansas City, MO; and Tulsa, AL. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.**

```{r}
homic <- homic %>% 
  filter(!city_state %in% c("Dallas,TX","Phoenix,AZ", "Kansas City,MO", "Tulsa,AL")) %>%
  filter(victim_race != "Unkonwn") %>% 
  mutate(victim_race = fct_relevel(ifelse(victim_race == "White", "white", "non-white"), "white")) %>%
  mutate(victim_age = as.numeric(victim_age))
```

**For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of  glm as an R object; apply the broom::tidy to this object**

```{r}
baltm <- homic %>% 
  filter(city_state == "Baltimore,MD")

baltm_glm <- glm(hmc_resolve ~ victim_age + victim_sex + victim_race, data = baltm, family = binomial()) %>% 
  broom::tidy()
baltm_glm
```

**Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed**

```{r}
baltm_glm <- baltm_glm %>% 
  mutate(or = exp(estimate),
         confint_low = exp(estimate - std.error*1.96),
         confint_up = exp(estimate + std.error*1.96)) %>% 
  select(term, estimate, or, confint_low, confint_up) %>% 
  knitr::kable(digits = 3)
baltm_glm
```

Description here

**Run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims**

```{r}
homic_city <- homic %>% 
  group_by(city_state) %>% 
  nest()

homic_city$glm_model <- map(homic_city$data, ~broom::tidy(glm(hmc_resolve ~ victim_age + victim_sex + victim_race, data = .x, family = binomial()))) 

homic_city <- homic_city %>% 
  select(city_state, glm_model) %>% 
  unnest() %>%
  filter(term == "victim_racenon-white") %>% 
  mutate(or = exp(estimate),
         confint_low = exp(estimate - std.error*1.96),
         confint_up = exp(estimate + std.error*1.96)) %>% 
  select(city_state, term, estimate, or, confint_low, confint_up)

```

**Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot**

```{r}
homic_city_plot <- homic_city %>%
  mutate(city_state = fct_reorder(city_state, or)) %>% 
  ggplot(aes(x = city_state, y = or)) +
  geom_point() +
  geom_errorbar(mapping = aes(ymin = confint_low, ymax = confint_up)) + 
  labs(
    title = "The estimated odds ratio and confidence interval for solving homicides comparing non-white victims to white victims in each city",
    x = "City, state",
    y = "Odds ratio"
  ) +
  theme(axis.text.x = element_text(angle = 90, size = 8),
        title = element_text(size = 6)) 

homic_city_plot
```

## Problem 2

```{r}
bw <- read_csv("./data/birthweight.csv")
```























































